From Topics to Opinions: \\Modelling Subjectivity for Retweeting Analysis on Twitter

### 2014-04-15 response.txt

We are very excited to have been given the opportunity to respond to reviews of our manuscript, We carefully considered comments offered by the three reviewers. We want to extend our appreciation for taking the time and effort necessary to provide such insightful guidance. Herein, we respond and explain how we revise the paper based on those comments and recommendations.
Responses to the comments of Reviewer #1 
1. [I don't see it as being impactful or of general interest to the AI community.] 
 Response: We apologize for the confusion caused because we haven't state the motivation and significance of our work clearly. In fact, we have investigated the reason why one diffuses information by modelling the subjectivity of a person with state-of-the-art AI researches. Specifically, we adopt topic model and sentiment analysis techniques of NLP to find latent clues such as topics and opinions from user-generated content, and use machine learning algorithms to train and predict based on the data we collect from Twitter. But the data may not constraint to social media, the model we have proposed can be adapted to other resources which can be used to mine the interests and opinions of users. The comment is very valuable and reminds us to make it more clear in the revision of the paper. 
2. [The clarity of the paper had some problems.]
Response:Thank you very much for such insightful comment and the problems are fixed during the revision of our paper.

Responses to the comments of Reviewer #2 
[several problems in the section where the subjectivity similarity is presented and defined.]
Response: Thank you for listing all the problems. In the revision, we have fixed all of them, and answered all the questions in our paper. 
In the topic similarity in (6), theta_m and theta_u are parameters learnt by LDA model representing topic distributions of users m and u;
In opinion similarity (7), d_i is the i^{th} entry of opinion distribution vector, and v_i denotes corresponding sentiment strength value, in the example of opinion distribution O^2, d_7=1.0, v_7=7;
The subjectivity similarity (9) is the general definition of subjectivity similarity among tweets, authors and followers, where parameters u and m may represent tweets, or authors, or followers;
In the Retweeting analysis paragraph, the sim_{sub} functions with  parameters represent subjectivity similarity between tweet and author, between tweet and a follower, and between author and a follower.

Responses to the comments of Reviewer #3
[the paper lacks comparison with Topic Sentiment Mixture (TSM) models.]
Response:This is a great point, We have cited this model in the related works, which is a very interesting work on sentiment analysis, and proved very useful especially in blogsphere. However, we didn't clearly clarify the diffrent between our model and TSM.
We will refine our paper to make the comparison more clear as follow.Sentiment analysis of tweets is more complicated than blogs or reviews. While TSM model try to train a general word-sentiment distribution model to determine the sentiment toward a topic, sentiment of a tweet is determined not only by normal words but also by the special characteristics of Twitter language such as emoticon, capitalized words，repeated letters, exclamation mark, which can not be easily modeled with probabilistic distribution, but can be modeled by transforming them to rules as Sentistrength has done. So we think that our method can better adapt to Twitter language and output more precise sentiment of a tweet. Besides, we want to get a more fine-grained sentiment to reflect the subtle opinion similarity, and the TSM model can only give relative coverage of the neurtral, positive, and negative opinions. But it is a good suggestion for our future research to realize our model in a mixture way as TSM by combining the characteristics of tweets, and we will compare such a model with TSM model.

### 2014-04-15 response_0321.txt

We appreciate the thorough reviews by the reviewers. Here are our responses:
Responses to Review 1:
1.The motivation of this research is to develop a new AI approach to investigate why one diffuses. Specifically, we adopt the topic model and sentiment analysis techniques in NLP to find latent clues such as  topics and opinions from user-generated contents, and use machine learning algorithms to train and predict on the data collected from Twitter. Obviously, this method we have proposed can be applied not only to social media, but also to other resources such as comments and news to mine the interests and opinions of users. These are impactful or of general interest to the AI community. We will further clarify the motivation more clearly in the revision of the manuscript.
2.For the problems of clarity, We will carefully revise the manuscript to make it clear.

Responses to Review 2:
1.We will fix and explain all the problems about the subjectivity similarity in the revision. 
Specifically, in (6), theta_m and theta_u are parameters learnt by LDA model representing topic distributions of users m and u;
In (7), d_i is the i^{th} entry of opinion distribution, and v_i denotes corresponding sentiment strength value, in the example of opinion distribution O^2, d_7=1.0, v_7=7;
The (9) is the general definition of subjectivity similarity among tweets, authors and followers, where u and m may represent tweets, or authors, or followers;
In the Retweeting analysis paragraph, sim_{sub} with different parameters represent different subjectivity similarity between tweet and author, between tweet and a follower, and between author and a follower;
sim_all represents all three subjectivity similarities used in the classifier.
2. All the spelling errors will be corrected in the revision.

Responses to Review 3:
Sentiment of tweets is determined not only by normal words but also by the special characteristics of Twitter languages such as emoticon, capitalized words, repeated letters and exclamation mark, etc. They can not be easily modelled with probabilistic distribution. TSM tries to learn a general word-sentiment distribution to model the sentiment of blogs, which may not work well for tweets. However, rule-based sentiment analysis methods can catch subtle sentiment of tweets by transforming these characteristics to rules. Therefore, we construct our model by combining the results of a LDA topic model and a rule-based sentiment classifier. TSM is a major approach that is closest to our work, we will cite and analysis it in our manuscript. And We will pursue it in the near future to carry out series of experiments to compare it with our method.

### 2014-04-15 response_0322-f.txt

We appreciate the detailed comments by the reviewers. Here are our responses:

Responses to Review 1:

1. We agree that the motivation of the research need to be more clearly explained.The motivation of this research is to develop a novel approach to investigate why one diffuses information. Specifically, we adopt the topic model and sentiment analysis techniques in NLP to find latent clues such as topics and opinions from user-generated contents, and use machine learning algorithms to train and predict on the data collected from Twitter. The proposed method can be applied not only to social media, but also to other resources such as user comments to mine the interests and opinions of users. Thus, the work is expected to be impactful or of general interest to the AI community. We will further clarify the motivation more clearly in the revision of the manuscript.
2.For the problems of clarity, We will carefully revise the manuscript to make it clear.

Responses to Review 2:

1.We agree that the explanation of the subjectivity similarity definition need to be revised to make it more clear in the revision. We will fix the problems and clarify some details as indicated by the reviewer.  
Specifically, in (6), theta_m and theta_u are parameters learnt by LDA model representing topic distributions of users m and u;
In (7), d_i is the i^{th} entry of opinion distribution, and v_i denotes corresponding sentiment strength value, in the example of opinion distribution O^2, d_7=1.0, v_7=7;
 (9) is the general definition of subjectivity similarity among tweets, authors and followers, where u and m may represent tweets, or authors, or followers;
In the retweeting analysis paragraph, sim_{sub} with different parameters represent different subjectivity similarity between tweet and author, between tweet and a follower, and between author and a follower;
sim_all represents all three subjectivity similarities used in the classifier.

2. All the spelling errors will be corrected in the revision.

Responses to Review 3:
Sentiment of tweets is determined not only by normal words but also by various special characteristics of Twitter languages such as emoticon, capitalized words, repeated letters and exclamation mark, etc. Those features cannot be easily modeled by a probabilistic distribution. TSM tries to learn a general word-sentiment distribution to model the sentiment of blogs, which may not work well for tweets. However, rule-based sentiment analysis methods can catch some subtle sentiment of tweets by transforming these characteristics into rules. Therefore, we construct our model by combining the results of a LDA topic model and a rule-based sentiment classifier. TSM is a major approach that is closest to our work, we will cite and review it in our revision. And We will pursue it in the near future to carry out series of experiments to compare it with our method.

### 2014-04-15 response_f.txt

After carefully considering comments offered by the three reviewers, We want to extend our appreciation for taking the time and effort necessary to provide such insightful guidance.
Responses to the comments of Reviewer #1 
1. [I don't see it as being impactful or of general interest to the AI community.] 
 Response: We apologize for the confusion caused because we haven't state the motivation and significance of our work clearly. In fact, we have investigated the reason why one diffuses information by modelling the subjectivity of a person with state-of-the-art AI researches. Specifically, we adopt topic model and sentiment analysis techniques of NLP to find latent clues such as topics and opinions from user-generated content, and use machine learning algorithms to train and predict on the data collected from Twitter. But the data may not constraint to social media, the model we have proposed can be adapted to other resources which can be used to mine the interests and opinions of users. The comment is very valuable and reminds us to make it more clear in the revision of the paper. 
2. [The clarity of the paper had some problems.]
Response:Thank you very much for such insightful comment and the problems are fixed during the revision of our paper.

Responses to the comments of Reviewer #2 
1.[problems in the section where the subjectivity similarity is presented and defined.]
Response: Thank you for listing all the problems. We have fixed all of them, and answered all the questions about the similarity in the revision.
2.[minor comments for spelling errors]
Response: Thank you for pointing out all the spelling errors, we have corrected all of them.

Responses to the comments of Reviewer #3
[the paper lacks comparison with Topic Sentiment Mixture (TSM) models.]
Response:This is a great point, we have cited TSM model in the related works, which is a very interesting work on topic related sentiment analysis in blogsphere. However, there is some difference between our work and TSM. We will refine our paper to make the comparison more clear as follows. Sentiment analysis of tweets is more complicated than blogs. While TSM try to train a general word-sentiment distribution model to determine the sentiment, sentiment of tweets is determined not only by normal words but also by the special characteristics of Twitter languages such as emoticon, capitalized words，repeated letters and exclamation mark, which can not be easily modeled with probabilistic distribution, but can be modeled by transforming them to rules as Sentistrength has done. So we think that our method can better adapt to Twitter and output more precise sentiment of tweets. Besides, we want to get a more fine-grained sentiment to reflect the subtle opinion similarity, and the TSM model can only give relative coverage of the neurtral, positive, and negative opinions. But it is good suggestion for our future research to construct our model in the way as TSM by combining the characteristics of tweets, and we will compare such a model with TSM model.

### 2014-04-15 response_kw.txt

Thank you for your detailed comments. We would like to response to some questions raised in the reviews as follows.

Responses to the comments in Review 1:
We agree that the work could be motivated better. The major challenge tackled in the paper is to diffuse Web information (from Twitter) by modelling the subjectivity of a user with state-of-the-art technologies from natural language processing (NLP). Specifically, we adopt topic model and sentiment analysis techniques in NLP to find latent clues such as topics and opinions from user-generated content, and use machine learning algorithms to train and predict on the data collected from Twitter. But the data may not constraint to social media. Actually, the model we have proposed can be adapted to other data resources and can be used in mining the interests and opinions of users.
We will improve the presentation following your comments.

Responses to the comments in Review 2:
We have fixed all of them, and answered all the questions about the similarity in the revision

Responses to the comments in Review 3:
TSM cited in the paper is a major approach that is closest to our work.
The TSM paper focuses on blogs but sentiment analysis of tweets is more challenging than that of blogs. While TSM try to train a general word-sentiment distribution model to determine the sentiment, sentiment of tweets is determined not only by normal words but also by the special characteristics of Twitter languages such as emoticon, capitalized words, repeated letters and exclamation mark, etc. They can not be easily modelled with probabilistic
distribution, but can be modelled by transforming them to rules as Sentistrength has done. So we think that our method is more suitable for Twitter and can catch more precise sentiment of tweets. Besides, we want to get a more fine-grained sentiment to reflect the subtle opinion similarity, but TSM model can only give relative coverage of neutral, positive, and negative opinions. It is an interesting idea to construct our model in the way as TSM by 
combining the characteristics of tweets, and we will compare such a model with TSM model. We will pursue it in the near future.

wrl：

We appreciate the thorough reviews be the reviewers. Here are our responses:

Responses to the comments of Reviewer #1
1. [I don't see it as being impactful or of general interest to the AI
community.]
Response: Thanks for your comments. The motivation of this research is develop a new AI approach to investigate why one diffuses. Specifically, we adopt the topic model and sentiment analysis techniques in NLP to find latent clues such as topics and opinions from user-generated contents, and use machine learning algorithms to train and predict on the data collected from Twitter. Obviously, this method we have proposed can be applied not only to social media, but also to  other resources such as to mine the interests and opinions of users. These are impactful or of general interest to the AI community. We will further clarify the motivation in the revision of the manuscript.
2. [The clarity of the paper had some problems.]
Response:  We will carefully revise the manuscript to make it clear.
Responses to the comments of Reviewer #2
1.[problems in the section where the subjectivity similarity is
presented and defined.]
Response:We have fixed all the problems listed by the reviewer about the similarity in the revision.
2.[minor comments for spelling errors]
Response: Thank you for pointing out all the spelling errors, which will be corrected in the revision.
Responses to the comments of Reviewer #3
[the paper lacks comparison with Topic Sentiment Mixture (TSM) models.]
Response: This is a great point, we have cited TSM model in the related
works, which is a very interesting work on topic related sentiment
analysis in blogsphere. However, there is some difference between our
work and TSM. We will refine our paper to make the comparison more clear
as follows. Sentiment analysis of tweets is more complicated than blogs.
While TSM trie to train a general word-sentiment distribution model to
determine the sentiment, sentiment of tweets is determined not only by
normal words but also by the special characteristics of Twitter
languages such as emoticon, capitalized words, repeated letters and
exclamation mark, which can not be easily modeled with a probabilistic
distribution, but can be modeled by transforming them to rules as
Sentistrength has done. Thus,we think that our method can better adapt to
Twitter and output more precise sentiment of tweets. Besides, we want to
get a more fine-grained sentiment to reflect the subtle opinion
similarity, and the TSM model can only give relative coverage of the
neutral, positive, and negative opinions. But it is good suggestion for
our future research to construct our model in the way as TSM by
combining the characteristics of tweets, and we will compare such a
model with TSM model.
